### 2020-01-22 ChapterImplementation/chapterImplementation.tex
Added: New diagrams for Implementation. Introduciton paragraph to Implementation and start of discussion of topology

\chapter{Implementation}
This section will discuss an implementation of AP using PhysX and RakNet.

@@

\section{System Architecture}
The simulation space is partitioned into regions, with each region consisting of its own instance of PhysX running on a dedicated GPU-enabled machine in the cloud. The boundary between regions is defined as a vertical plane, two-dimensionally dividing the simulation space into one region per server. The network library RakNet is used for all message passing between servers. RakNet ensures messages exhibit best effort and are received in sent order.

@@

When objects traverse region boundaries, they are added to a migration buffer with all information required to duplicate an object at a neighbouring server. The contents of a migration buffer are sent to a server now responsible for hosting an object. When migration messages are received an object is created within the server's simulation.
% ^^^^ Replace 'an' with 'each'?

Clients may connect to any server and are provided with a streamed visualisation of the simulation in real-time. Clients may also interact with and influence the simulation, providing a comprehensive solution for real-time interactive physics. The client system was built using the Unreal Engine. Once a client is connected, the position and states (replicas) of all objects in the simulation are sent from each server to the client via the RakNet Replica Manager.

\begin{figure}[!t]
	\centering
	\includegraphics[width=\textwidth]{ArchitectureDiagramVertical}
	\caption{Server Architecture}
	\label{fig_stack}
\end{figure}

>>>>

\chapter{Implementation}
In this section will discuss our implementation of AP, The following will be looked at in detail: \begin{itemize}
	\item An overview of the system architecture: How the servers are deployed in the cloud and how they communicate with a client, along with potential deployments to be investigated in the future.
	\item A breakdown of the components of each server.
	\item The algorithms used by the servers to implement AP.
	\item The life cycle of a simulated object as a finite state machine (FSM).
	\item The features and implementation details of the visualiser, including a breakdown of the components of a client and future work to be carried out on the visualiser.
\end{itemize}

@@

\section{System Architecture}
%TODO: Mention we're using AWS EC2 G2 instances
The simulation space is partitioned into regions, with each region consisting of its own instance of PhysX running on a dedicated GPU-enabled machine in the cloud. The boundary between regions is defined as a vertical plane, two-dimensionally dividing the simulation space into one region per server. The network library RakNet is used for all message passing between servers. RakNet ensures messages exhibit best effort and are received in sent order.

@@

When objects traverse region boundaries, they are added to a migration buffer with all information required to duplicate an object at a neighbouring server. The contents of each migration buffer are sent to the associated server, which will then be responsible for hosting the migrated objects. When migration messages are received, the migrated objects are created within the receiving server's simulation.

Clients connect to all servers and are provided with a streamed visualisation of the simulation in real-time. Clients may also interact with and influence the simulation through client-created replicas and static objects, and RPCs, providing a comprehensive solution for real-time interactive physics. The client system was built using the Unreal Engine. Once a client is connected, the position and states (replicas) of all objects in the simulation are sent from each server to the client via the RakNet Replica Manager.

\begin{figure}[h]
	\centering
	\scalebox{1.5}{\input{Figs/OurDeploymentV2.pdf_tex}}
	\caption{Network Topology. Each server is an EC2 instance in the cloud, running our implementation of AP, which includes an instance of PhysX. The client is a local machine running the visualiser built in Unreal Engine. Servers connect to each other in order to exchange messages for aura creation/update and deletion and the migration of objects. The client receives replica updates from each server as well as sending client-created replicas and static objects, and RPCs.}
\end{figure}

\subsection{Server-Region Topology}
Server-region topologies and how they affect the communication requirements between servers will now be discussed. 
AP allows for the simulation space to be partitioned into any topology. In terms of communication, all servers need to communicate with all of their neighbours in order to satisfy the solution to the corner case, as described in \ref{CornerCase}. We define a neighbour as any server that shares a region boundary, including at a corner. The simplest topology that can be used is a column layout, as shown in \ref{ServerColumnLayout}. In column layout, servers have at most two neighbours, this topology therefore has the fewest server connection requirements.

\definecolor{rvwvcq}{rgb}{0.08235294117647059,0.396078431372549,0.7529411764705882}
\definecolor{sim}{rgb}{0,0.2,0.5}
\begin{figure}[!t]	\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=1.5]
	\clip(-2.25,0) rectangle (8.4,3.75);
	\fill[line width=0.8pt,color=sim,fill=sim,fill opacity=0.1] (-2.25,3) -- (-2.25,0) -- (8.25,0) -- (8.25,3) -- cycle;
	\draw (-1.5,3.5) node[anchor=center] {Server 0};
	\draw (1.5,3.5) node[anchor=center] {Server 1};
	\draw (4.5,3.5) node[anchor=center] {\textbf{...}};
	\draw (7.5,3.5) node[anchor=center] {Server N-1};
	\draw [line width=2pt] (0,0)-- (0,3);
	\draw [line width=2pt] (3,0)-- (3,3);
	\draw [line width=2pt] (6,0)-- (6,3);
	\end{tikzpicture}
	\centering
	\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm]
	\clip(-4,0) rectangle (7,1.5);
	\draw [line width=2pt] (-0.5,0.7)-- (-0.3,0.7);
	\draw (-0.1,0.7) node[anchor=west] {Server-Region Boundary};
	\end{tikzpicture}
	\caption{Column Layout}
	\label{ServerColumnLayout}
\end{figure}

\begin{figure}[!t]
	\begin{subfigure}{.5\textwidth}
		\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=1.2]
		\fill[line width=0.8pt,color=sim,fill=sim,fill opacity=0.1] (-3,3) -- (-3,-2) -- (3,-2) -- (3,3) -- cycle;
		\draw [line width=2pt] (-3,0)-- (3,0);
		\draw [line width=2pt] (0,3)-- (0,0);
		\draw (-1.5,2.5) node[anchor=center] {Server 0};
		\draw (1.5,2.5) node[anchor=center] {Server 1};
		\draw (0,-1) node[anchor=center] {Server 2};
		\end{tikzpicture}
		\centering
		\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm]
		\draw [line width=2pt] (-2.5,0.5)-- (-2.3,0.5);
		\draw (-2.1,0.5) node[anchor=west] {Region Boundary};
		\end{tikzpicture}
		\caption{3 Server Corner Layout}
		\label{3ServerCornerLayout}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=1.2]
		%	\clip(-3,-3) rectangle (3,3);
		\fill[line width=0.8pt,color=sim,fill=sim,fill opacity=0.1] (-3,3) -- (-3,-3) -- (3,-3) -- (3,3) -- cycle;
		\draw [line width=2pt] (-3,0)-- (3,0);
		\draw [line width=2pt] (0,3)-- (0,0);
		\draw (-1.5,2.5) node[anchor=center] {Server 0};
		\draw (1.5,2.5) node[anchor=center] {Server 1};
		\draw (-1.5,-2.5) node[anchor=center] {Server 2};
		\draw (1.5,-2.5) node[anchor=center] {Server 3};
		\draw [line width=2pt] (0,0)-- (0,-3);
		\end{tikzpicture}
		\centering
		\caption{4 Server Corner Layout}
		\label{4ServerCornerLayout}
	\end{subfigure}
	\caption{Corner Layouts}
	\label{ServerCornerLayout}
\end{figure}

\subsection{Individual Server Breakdown}

\begin{figure}[h]
	\centering
	\resizebox{\linewidth}{!}{\input{Figs/Architecture.pdf_tex}}
	%\scalebox{1.1}{\input{Figs/Architecture.pdf_tex}}
	\caption{Server Breakdown. This diagram shows a breakdown of the components of an individual server.}
	\label{fig_stack}
\end{figure}

\subsection{Future Architecture}

\begin{figure}
	\centering
	\scalebox{1.25}{\input{Figs/OverseerNode.pdf_tex}}
	\caption{Overseer node.}
\end{figure}

\begin{figure}
	\centering
	\scalebox{1.25}{\input{Figs/MultipleOverseerNodes.pdf_tex}}
	\caption{Multiple overseer nodes for scalable number of players.}
\end{figure}

\begin{figure}
	\centering
	\scalebox{1.25}{\input{Figs/EdgeBasedOverseerNodes.pdf_tex}}
	\caption{Edge-based overseer nodes.}
\end{figure}

\begin{figure}
	\centering
	\scalebox{1.25}{\input{Figs/DedicatedRenderNodes.pdf_tex}}
	\caption{Dedicated render nodes in cloud.}
\end{figure}

\begin{figure}
	\centering
	\scalebox{1.25}{\input{Figs/EdgeBasedRenderNodes.pdf_tex}}
	\caption{Dedicated render nodes in edge.}
\end{figure}
